Individual heterogeneity in the functional network topography of medial prefrontal

### 2019-09-06 Manuscript.Rmd
results ready, onto discussion revisions now

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures. Area 25 (in red) was disregarded because of the possible confound with projections from spheres located in ventral striatum (see text for details). Areas in blue represent the remainder of the search space."}
# brain images were produced using the HCP wb_view. 
# see the function HCPOut for details on how they were transferred from R to CIFTI
include_graphics("./Images/ROIS.png")
```

@@

```{r Representative partitioning (Fig. 2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with red areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
include_graphics("./Images/FB_FV_example.png")
```

@@

``` {r Partitioning comparison: all (Fig. 3), fig.align="center", out.width = "50%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. Functional topographic patterns were better aligned across individuals in PCC than mPFC.", echo=FALSE, message = FALSE}
# code to produce the plot
# par(xpd = T)
# corrplot(abs(RI_PCC), # absolute for display purposes only, as it avoids the couple of negative ARIs and evens out the color bar
#          is.corr = F, 
#          method = "color",
#          type = "lower", 
#          tl.pos = "n", 
#          tl.cex = 0.1, 
#          cl.lim = c(0,1),
#          cl.length = 3,
#          #addgrid.col = "grey99",
#          cl.pos = "r",
#          mar = c(1,1,2,0))
# corrplot(RI_PFC, 
#          is.corr = F, 
#          method = "color", 
#          type = "upper", 
#          tl.pos = "n", 
#          tl.cex = 0.1,
#          cl.pos = "n",
#          #addgrid.col = "grey90",
#          mar = c(1,1,2,0), 
#          add = T)
# segments(0.5,0.5,0.5,100.5, lwd = 2)
# segments(0.5,0.5,100.5,0.5, lwd = 2)
# segments(0.5,100.5,100.5,100.5, lwd = 2)
# segments(100.5,0.5,100.5,100.5, lwd = 2)
# mtext(expression(bold("Subject Partitions")), line = 3)
# mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
# mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
# mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Variability per subject: Fiedler vector vs prop. DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs). B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (lower). The maps share considerable qualitative similarities in their gradients along the cortical surface. C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations. Grey lines display data for each subject, and the black line shows the fit from a mixed-effects logistic regression. Dashed red lines indicate the mean FV value at which maps were thresholded. The histogram displays the mean frequency distribution of y-axis values.", echo=FALSE, message = FALSE}
# code to generate plots

@@

```{r Thresholded maps (Fig 5), out.height = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector map for subject 100307 (top), and its binarized form (bottom). Subthreshold values effectively formed a third community of high-variability vertices. B: Mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample. Colors represent PCC-based labels ('DN' versus 'non-DN'), which were applied in a subsequent step following the data-driven community-detection analysis and which were necessarily well-aligned in PCC. This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the high level of variability in mPFC."}

@@

``` {r Partition comparison: halves and runs (Fig. 6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 scanning days each), showing pattern agreement across days and subjects for PCC and mPFC separately. Color scale represents the ARI, which quantifies topographic similarity irrespective of how the communities are labeled. The block-diagonal structure is indicative of test-retest reliability across days within an individual. Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncratic community arrangement for both PCC and mPFC (ratios > 1, solid line), with greater subject-specificity in mPFC. Right: within-to-between subject mean ARI ratios for run-specific partitionings again show greater subject-specific organization for mPFC.", echo=FALSE, message = FALSE}
### code for plots in this fig

@@

``` {r Correlation vs community detection (Fig. 7), fig.align = "center", fig.cap = "A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects. The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector, with two single-day-based maps per individual. The upper-right and lower-left quadrants show across-method agreement. B: Day 1 vs Day 2 within-subject correlation coefficients for each method, as well as between methods. Community detection through spectral partitioning provided more stable estimates, even though both methods showed good levels of agreement.", echo = FALSE, message = FALSE}
# code to produce the plots

@@

We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the one used by Lopez-Persem et al. [-@Lopez2019], a superior mPFC zone (sup-mPFC) that contained the remaining dorsal mPFC regions, and PCC (Figure 8B, left). For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere. Negative correlations in this context imply that the DN was likely found in sulci and non-DN in gyri. Results can be found on Figure 8B. We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`). Correlations between FV and curvature were positive and significantly different than zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC. Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`). The difference across hemispheres was significant (paired t-test: t = `r curvPCC_t$statistic`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`). These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al. [-@Lopez2019], and suggest that the association between function and structure is heterogenous within canonical DN.

```{r Association with sulci (Fig. 8), fig.align = "center", fig.cap = "A: Correspondence between SP communities and sulcal morphology in two example individuals. Zoomed-in boxes show areas in PCC and ventral mPFC where the DN community appears to be guided by sulcal organization. This relationship is less defined in superior mPcFC. The superior rostral sulcus houses the DN community, in agreement with findings by Lopez-Persem et al. (2019). B: Correlations between cortical curvature and the unthresholded Fiedler values. We divided the search space into three areas (left): ventral mPFC (yellow), superior mPFC (sup-mPFC, red), and PCC (blue). Boxplots on the right show the distribution of correlation values across individuals for each combination of region and hemisphere, indicating that DN (signaled by positive FV values) tended to be represented in vmPFC sulci, but was likely located in gyri within sup-dmPFC. PCC had an inversed relationship across hemispheres, with DN landing more often in left hemisphere sulci."}
# # box plot
# curvCors %>%  ggplot(aes(Hemisphere, Correlation, fill = region)) +
#   geom_hline(yintercept = 0, linetype = "dashed", size = 1.2) +
#   geom_boxplot(show.legend = F, size = 1.5) +
#   geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
#   scale_fill_manual(values = c("dodgerblue4", "firebrick", "gold2")) +
#   labs(y = "Correlation") +
#   guides(color = F) +
#   facet_wrap(vars(region), ncol = 3) +
#   theme(legend.position = c(0.85, 0.7),
#         legend.key=element_blank(),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank(),
#         axis.line = element_line(colour = "black"),
#         text = element_text(size = 22))

@@

@@

Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A. However, the non-DN community filled areas not covered by either DN-A or DN-B. This result supports the idea that the two approaches serve complementary purposes. Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.

```{r BandB comparison (Figure 9), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (estimated based on descriptions from Braga et al. (2019)) and SP communities for two individuals. Panel A: Whole-brain networks A and B produced by selecting seeds in TPJ, with our community detection search space delineated by black borders. Correlation values are thresholded at 0.2. Panel B: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A. The non-DN community covers sections of cortex not associated with either DN sub-network."}

@@

```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings. The first two columns show both Fiedler vector values  and binarized communities, respectively. A common organizational principle is visible, even though it shifts topographically across individuals. The organization is also evident when using Modularity (third column), even though some isolated vertices were sometimes placed in a small third community (see subject 100408). The fourth column shows Fiedler vector maps after adding adding retrosplenial cortex (a common component of canonincal DN affected by task-deactivation). The addition of this area to the search space does not alter the original results, and the region is adequately covered by the DN community."}
include_graphics("./Images/extra_examples.png")
```

@@

```{r ARI Comparison (supplemental fig 2), out.width = "100%", fig.align = "center", fig.cap = "A: Example of an across-day comparison using ARI for two subjects (100307 and 100408). This reflects how qualitatively similar, within-subject partitionings can have relatively small ARI values (here 0.24-0.25), and how partitionings across individuals are much closer to the chance level of zero. B: Simulated comparison between two binary partitionings. The allegiance of each node is progressively switched, and the agreement between the new vector and the original one is computed on each change. The x-axis shows the number of nodes switched. Comparing the increasingly dissimilar maps by computing the proportion of equal cluster labelings (EQ) shows the expected linear decrease in similarity. The unadjusted form of the ARI (RI) displays an exponentially decaying similarity, and increases after reaching 50% as a result of node pairs once again being grouped in the same/different clusters (making the index label-agnostic). The ARI decays more dramatically as a function of increasing dissimilarity, reaching 0 at chance levels. Low ARI values can therefore still occur when there is notable agreement between partitionings."}

@@

```{r tSNR (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Signal quality prior to FV thresholding. Left: Surface map displaying the vertex-wise mean tSNR across individuals. Right: Mean tSNR for mPFC and PCC across individuals."}
# To get the box plot:
#   
# allSnr <- list()
# 
# for (i in seq_along(Summaries)) {
#   
#   allSnr[[i]] <- Summaries[[i]] %>% 
#                   mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
#                   group_by(region) %>%
#                   summarise(mtSNR = mean(tSNR))
#                 
# }
# 
# allSnr <- do.call(rbind, allSnr)
# 
# ggplot(data = allSnr, aes(region, mtSNR, fill = region)) + 
#   geom_boxplot(show.legend = F) +
#   scale_fill_manual(values = Cols[seq(2)]) +
#   labs(x = "", y = "mean tSNR") +
#   theme(legend.position = c(0.9, 0.32),
#         legend.key=element_blank(),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank(),
#         axis.line = element_line(colour = "black"),
#         text = element_text(size = 22))

@@

```{r day- and run-wise brain comparisons (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Visual examples of idiosyncratic organization across days and runs. Left: Thresholded partitionings captured with SP are highly similar across days within individuals, but are topographically distinct across individuals. The organization estimated for each dat is also mostly indistinct from that captured using the full time series (Supplemental Figure 1). Right: Thresholded partitionings estimated using the first scanning session from day 1, and the last scanning session from day 2. As expected, the considerable reduction in the amount of data used decreased the reliability of the community localization across single scanning sessions, which were in some cases irrecoverable (e.g. subjects 100408 and 687163). Even so, the general location of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data. This shows that even with notably noisier estimates and lower within-individual ARI values produced by working with less data, it is possible to gain information about the general location of DN and non-DN in individuals."}
include_graphics("./Images/days_runs_examples.png")
```

>>>>

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1. Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures. Area 25 (in red) was disregarded because of the possible confound with projections from spheres located in ventral striatum (see text for details). Areas in blue represent the remainder of the search space."}
# brain images were produced using the HCP wb_view. 
# see the function HCPOut for details on how they were transferred from R to CIFTI
include_graphics("./Images/ROIS.png")
```

@@

```{r Representative partitioning (Fig. 2), out.width = "50%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with red areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
include_graphics("./Images/FB_FV_example.png")
```

@@

``` {r Partitioning comparison: all (Fig. 3), fig.align="center", out.width = "50%", fig.cap = "Figure 3. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. Functional topographic patterns were better aligned across individuals in PCC than mPFC.", echo=FALSE, message = FALSE}
# code to produce the plot
# par(xpd = T)
# corrplot(abs(RI_PCC), # absolute for display purposes only, as it avoids the couple of negative ARIs and evens out the color bar
#          is.corr = F, 
#          method = "color",
#          type = "lower", 
#          tl.pos = "n", 
#          tl.cex = 0.1, 
#          cl.lim = c(0,1),
#          cl.length = 3,
#          #addgrid.col = "grey99",
#          cl.pos = "r",
#          mar = c(1,1,2,0))
# corrplot(RI_PFC, 
#          is.corr = F, 
#          method = "color", 
#          type = "upper", 
#          tl.pos = "n", 
#          tl.cex = 0.1,
#          cl.pos = "n",
#          #addgrid.col = "grey90",
#          mar = c(1,1,2,0), 
#          add = T)
# segments(0.5,0.5,0.5,100.5, lwd = 2)
# segments(0.5,0.5,100.5,0.5, lwd = 2)
# segments(0.5,100.5,100.5,100.5, lwd = 2)
# segments(100.5,0.5,100.5,100.5, lwd = 2)
# mtext(expression(bold("Subject Partitions")), line = 3)
# mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
# mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
# mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Variability per subject: Fiedler vector vs prop. DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 4. A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs). B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (lower). The maps share considerable qualitative similarities in their gradients along the cortical surface. C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations. Grey lines display data for each subject, and the black line shows the fit from a mixed-effects logistic regression. Dashed red lines indicate the mean FV value at which maps were thresholded. The histogram displays the mean frequency distribution of y-axis values.", echo=FALSE, message = FALSE}
# code to generate plots

@@

```{r Thresholded maps (Fig 5), out.height = "50%", fig.align = "center", fig.cap= "Figure 5. A: Thresholded Fiedler vector map for subject 100307 (top), and its binarized form (bottom). Subthreshold values effectively formed a third community of high-variability vertices. B: Mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample. Colors represent PCC-based labels ('DN' versus 'non-DN'), which were applied in a subsequent step following the data-driven community-detection analysis and which were necessarily well-aligned in PCC. This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the high level of variability in mPFC."}

@@

``` {r Partition comparison: halves and runs (Fig. 6), fig.align="center", out.width = "100%", fig.cap = "Figure 6. Left: Similarity matrix for 10 example participants (2 scanning days each), showing pattern agreement across days and subjects for PCC and mPFC separately. Color scale represents the ARI, which quantifies topographic similarity irrespective of how the communities are labeled. The block-diagonal structure is indicative of test-retest reliability across days within an individual. Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncratic community arrangement for both PCC and mPFC (ratios > 1, solid line), with greater subject-specificity in mPFC. Right: within-to-between subject mean ARI ratios for run-specific partitionings again show greater subject-specific organization for mPFC.", echo=FALSE, message = FALSE}
### code for plots in this fig

@@

``` {r Correlation vs community detection (Fig. 7), fig.align = "center", fig.cap = "Figure 7. A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects. The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector, with two single-day-based maps per individual. The upper-right and lower-left quadrants show across-method agreement. B: Day 1 vs Day 2 within-subject correlation coefficients for each method, as well as between methods. Community detection through spectral partitioning provided more stable estimates, even though both methods showed good levels of agreement.", echo = FALSE, message = FALSE}
# code to produce the plots

@@

```{r Association with sulci (Fig. 8), fig.align = "center", fig.cap = "Figure 8. A: Correspondence between SP communities and sulcal morphology in two example individuals. Zoomed-in boxes show areas in PCC and ventral mPFC where the DN community appears to be guided by sulcal organization. This relationship is less defined in superior mPcFC. The superior rostral sulcus houses the DN community, in agreement with findings by Lopez-Persem et al. (2019). B: Correlations between cortical curvature and the unthresholded Fiedler values. We divided the search space into three areas (left): ventral mPFC (yellow), superior mPFC (sup-mPFC, red), and PCC (blue). Boxplots on the right show the distribution of correlation values across individuals for each combination of region and hemisphere, indicating that DN (signaled by positive FV values) tended to be represented in vmPFC sulci, but was likely located in gyri within sup-dmPFC. PCC had an inversed relationship across hemispheres, with DN landing more often in left hemisphere sulci."}
# # box plot
# curvCors %>%  ggplot(aes(Hemisphere, Correlation, fill = region)) +
#   geom_hline(yintercept = 0, linetype = "dashed", size = 1.2) +
#   geom_boxplot(show.legend = F, size = 1.5) +
#   geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
#   scale_fill_manual(values = c("dodgerblue4", "firebrick", "gold2")) +
#   labs(y = "Correlation") +
#   guides(color = F) +
#   facet_wrap(vars(region), ncol = 3) +
#   theme(legend.position = c(0.85, 0.7),
#         legend.key=element_blank(),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank(),
#         axis.line = element_line(colour = "black"),
#         text = element_text(size = 22))

@@

We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the one used by Lopez-Persem et al. [-@Lopez2019], a superior mPFC zone (sup-mPFC) that contained the remaining dorsal mPFC regions, and PCC (Figure 8B, left). For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere. Negative correlations in this context imply that the DN was likely found in sulci and non-DN in gyri. Results can be found on Figure 8B. We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`). Correlations between FV and curvature were positive and significantly different than zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC. Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`). The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`). These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al. [-@Lopez2019], and suggest that the association between function and structure is heterogenous within canonical DN.

@@

Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A. However, the non-DN community filled areas not covered by either DN-A or DN-B. Since this three-network configuration is at odds with the two-network solution suggested in our previous analyses (i.e. comparison with modularity), we ran additional evaluations to confirm its existence. First, we reproduced the whole-brain k-means clustering analysis (n of clusters = 12, 100 iterations) performed by Braga et al. [-@Braga2019] in our two subjects using their full time series (Supplemental Figure 5A). In addition to identifying DN networks A and B through this approach (in line with their findings), we found a third cluster that aligned well with the non-DN community. To understand why we could not find this organization before, we performed a silhouette analysis to determine the ideal number of clusters in our search space (Supplemental Figure 5B). For every individual, we ran k-means clusterings with a specified number of clusters ranging from 2 to 5, and computed a silhouette score for each solution (higher silhouette scores indicate a better fit). Scores decreased as the number of clusters increased for all individuals, suggesting that a bisection was indeed the best solution. Paired permutations comparing mean scores across individuals indicated that the difference between two (mean = 0.042, SE = 0.001) and three (mean = 0.032, SE = 0.0009) cluster solutions was significant (*p* < 0.0001, Cohen's D = 0.96). Visualization of a two-cluster k-means revealed a close match with partitionings estimated through modularity, and are comparable to those produced by SP prior to thresholding (Supplemental Figure 5A, bottom rows). These analyses suggest that SP isolated DN-A and the non-DN community as the dominant opposite signals within our search space, but that DN-B is observable once we take advantage of the continuous information contained in the Fiedler vector.

These results supports the idea that the two approaches serve complementary purposes. Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex. Furthermore, they show that our approach can identify the three networks in a way that is less computationally demanding than full-brain clustering, outperforming other clustering methods that lack the continuous information provided by SP.

```{r BandB comparison (Figure 9), out.width = "100%", fig.align = "center", fig.cap= "Figure 9. Qualitative comparison between DN sub-networks A and B (estimated based on descriptions from Braga et al. (2019)) and SP communities for two individuals. Panel A: Whole-brain networks A and B produced by selecting seeds in TPJ, with our community detection search space delineated by black borders. Correlation values are thresholded at 0.2. Panel B: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A. The non-DN community covers sections of cortex not associated with either SP sub-network."}

@@

```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 1. Additional examples of individualized partitionings. The first two columns show both Fiedler vector values  and binarized communities, respectively. A common organizational principle is visible, even though it shifts topographically across individuals. The organization is also evident when using Modularity (third column), even though some isolated vertices were sometimes placed in a small third community (see subject 100408). The fourth column shows Fiedler vector maps after adding adding retrosplenial cortex (a common component of canonincal DN affected by task-deactivation). The addition of this area to the search space does not alter the original results, and the region is adequately covered by the DN community."}
include_graphics("./Images/extra_examples.png")
```

@@

```{r ARI Comparison (supplemental fig 2), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 2. A: Example of an across-day comparison using ARI for two subjects (100307 and 100408). This reflects how qualitatively similar, within-subject partitionings can have relatively small ARI values (here 0.24-0.25), and how partitionings across individuals are much closer to the chance level of zero. B: Simulated comparison between two binary partitionings. The allegiance of each node is progressively switched, and the agreement between the new vector and the original one is computed on each change. The x-axis shows the number of nodes switched. Comparing the increasingly dissimilar maps by computing the proportion of equal cluster labelings (EQ) shows the expected linear decrease in similarity. The unadjusted form of the ARI (RI) displays an exponentially decaying similarity, and increases after reaching 50% as a result of node pairs once again being grouped in the same/different clusters (making the index label-agnostic). The ARI decays more dramatically as a function of increasing dissimilarity, reaching 0 at chance levels. Low ARI values can therefore still occur when there is notable agreement between partitionings."}

@@

```{r tSNR (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 3. Signal quality prior to FV thresholding. Left: Surface map displaying the vertex-wise mean tSNR across individuals. Right: Mean tSNR for mPFC and PCC across individuals."}
# To get the box plot:
#   
# allSnr <- list()
# 
# for (i in seq_along(Summaries)) {
#   
#   allSnr[[i]] <- Summaries[[i]] %>% 
#                   mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
#                   group_by(region) %>%
#                   summarise(mtSNR = mean(tSNR))
#                 
# }
# 
# allSnr <- do.call(rbind, allSnr)
# 
# ggplot(data = allSnr, aes(region, mtSNR, fill = region)) + 
#   geom_boxplot(show.legend = F) +
#   scale_fill_manual(values = Cols[seq(2)]) +
#   labs(x = "", y = "mean tSNR") +
#   theme(legend.position = c(0.9, 0.32),
#         legend.key=element_blank(),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank(),
#         axis.line = element_line(colour = "black"),
#         text = element_text(size = 22))

@@

```{r day- and run-wise brain comparisons (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 4. Visual examples of idiosyncratic organization across days and runs. Left: Thresholded partitionings captured with SP are highly similar across days within individuals, but are topographically distinct across individuals. The organization estimated for each dat is also mostly indistinct from that captured using the full time series (Supplemental Figure 1). Right: Thresholded partitionings estimated using the first scanning session from day 1, and the last scanning session from day 2. As expected, the considerable reduction in the amount of data used decreased the reliability of the community localization across single scanning sessions, which were in some cases irrecoverable (e.g. subjects 100408 and 687163). Even so, the general location of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data. This shows that even with notably noisier estimates and lower within-individual ARI values produced by working with less data, it is possible to gain information about the general location of DN and non-DN in individuals."}
include_graphics("./Images/days_runs_examples.png")
```
